---
title: "actinALP"
output: html_notebook
---


```{r, message=FALSE}
library(magrittr)
library(stringr)
library(tidyverse)
```

## Load per-cell data

```{r}
load("ph_raw_data.RData")

object <- cell.ftrs

image <- image.data

rm(list = c("cell.ftrs", "image.data"))
```


```{r}

object %<>%
  inner_join(image %>% select(ImageNumber, FeatureIdx)) %>%
  ungroup()

```


## Predict  Actin total intensity given Actin standard deviation

For each surface, fit a linear model to predict total intensity of actin given the actin standard deviation, and plot the density of R^2 values, measured across all the surfaces.

```{r}
actin_sd <-
  object %>%
  split(.$FeatureIdx) %>%
  map(~ lm(Cells_Intensity_IntegratedIntensity_Actin4Corr ~ Cells_Intensity_StdIntensity_Actin4Corr, data = .)) %>%
  map(summary) %>%
  map_df("adj.r.squared") %>%
  gather(FeatureIdx, value)
  
ggplot(actin_sd, aes(value)) + 
  stat_density(adjust = 0.8, alpha = 0.5) + 
  xlab("Adjusted R^2 of prediction Actin total intensity given Actin standard deviation") + 
  xlim(-1, 1)

```


## Predict  Actin total intensity given cell shape 

For each surface, fit a linear model to predict total intensity of actin given the cell shape features, and plot the density of R^2 values, measured across all the surfaces.

```{r}
shape_area <- 
  object %>%
  split(.$FeatureIdx) %>%
  map(~ lm(Cells_Intensity_IntegratedIntensity_Actin4Corr ~ 
             Cells_AreaShape_Area +
             Cells_AreaShape_Center_X +
             Cells_AreaShape_Center_Y +
             Cells_AreaShape_Compactness +
             Cells_AreaShape_Eccentricity +
             Cells_AreaShape_EulerNumber +
             Cells_AreaShape_Extent +
             Cells_AreaShape_FormFactor +
             Cells_AreaShape_MajorAxisLength +
             Cells_AreaShape_MinorAxisLength +
             Cells_AreaShape_Orientation +
             Cells_AreaShape_Perimeter +
             Cells_AreaShape_Solidity +
             Cells_AreaShape_Zernike_0_0 +
             Cells_AreaShape_Zernike_1_1 +
             Cells_AreaShape_Zernike_2_0 +
             Cells_AreaShape_Zernike_2_2 +
             Cells_AreaShape_Zernike_3_1 +
             Cells_AreaShape_Zernike_3_3 +
             Cells_AreaShape_Zernike_4_0 +
             Cells_AreaShape_Zernike_4_2 +
             Cells_AreaShape_Zernike_4_4 +
             Cells_AreaShape_Zernike_5_1 +
             Cells_AreaShape_Zernike_5_3 +
             Cells_AreaShape_Zernike_5_5 +
             Cells_AreaShape_Zernike_6_0 +
             Cells_AreaShape_Zernike_6_2 +
             Cells_AreaShape_Zernike_6_4 +
             Cells_AreaShape_Zernike_6_6 +
             Cells_AreaShape_Zernike_7_1 +
             Cells_AreaShape_Zernike_7_3 +
             Cells_AreaShape_Zernike_7_5 +
             Cells_AreaShape_Zernike_7_7 +
             Cells_AreaShape_Zernike_8_0 +
             Cells_AreaShape_Zernike_8_2 +
             Cells_AreaShape_Zernike_8_4 +
             Cells_AreaShape_Zernike_8_6 +
             Cells_AreaShape_Zernike_8_8 +
             Cells_AreaShape_Zernike_9_1 +
             Cells_AreaShape_Zernike_9_3 +
             Cells_AreaShape_Zernike_9_5 +
             Cells_AreaShape_Zernike_9_7 +
             Cells_AreaShape_Zernike_9_9, 
           data = .)) %>%
  map(summary) %>%
  map_df("adj.r.squared") %>%
  gather(FeatureIdx, value)

ggplot(shape_area, aes(value)) + 
  stat_density(adjust = 0.8, alpha = 0.5) + 
  xlab("Adjusted R^2 of prediction Actin total intensity given cell shape") + 
  xlim(-1, 1)


```


Do the same thing as above but exclude any features that are indicative of size

```{r}

shape <- 
  object %>%
  split(.$FeatureIdx) %>%
  map(~ lm(Cells_Intensity_IntegratedIntensity_Actin4Corr ~ 
             Cells_AreaShape_Compactness +
             Cells_AreaShape_Eccentricity +
             Cells_AreaShape_EulerNumber +
             Cells_AreaShape_FormFactor +
             Cells_AreaShape_Orientation +
             Cells_AreaShape_Solidity +
             Cells_AreaShape_Zernike_1_1 +
             Cells_AreaShape_Zernike_2_0 +
             Cells_AreaShape_Zernike_2_2 +
             Cells_AreaShape_Zernike_3_1 +
             Cells_AreaShape_Zernike_3_3 +
             Cells_AreaShape_Zernike_4_0 +
             Cells_AreaShape_Zernike_4_2 +
             Cells_AreaShape_Zernike_4_4 +
             Cells_AreaShape_Zernike_5_1 +
             Cells_AreaShape_Zernike_5_3 +
             Cells_AreaShape_Zernike_5_5 +
             Cells_AreaShape_Zernike_6_0 +
             Cells_AreaShape_Zernike_6_2 +
             Cells_AreaShape_Zernike_6_4 +
             Cells_AreaShape_Zernike_6_6 +
             Cells_AreaShape_Zernike_7_1 +
             Cells_AreaShape_Zernike_7_3 +
             Cells_AreaShape_Zernike_7_5 +
             Cells_AreaShape_Zernike_7_7 +
             Cells_AreaShape_Zernike_8_0 +
             Cells_AreaShape_Zernike_8_2 +
             Cells_AreaShape_Zernike_8_4 +
             Cells_AreaShape_Zernike_8_6 +
             Cells_AreaShape_Zernike_8_8 +
             Cells_AreaShape_Zernike_9_1 +
             Cells_AreaShape_Zernike_9_3 +
             Cells_AreaShape_Zernike_9_5 +
             Cells_AreaShape_Zernike_9_7 +
             Cells_AreaShape_Zernike_9_9, 
           data = .)) %>%
  map(summary) %>%
  map_df("adj.r.squared") %>%
  gather(FeatureIdx, value)

ggplot(shape, aes(value)) + 
  stat_density(adjust = 0.8, alpha = 0.5) + 
  xlab("Adjusted R^2 of prediction Actin total intensity given cell shape excluding size") + 
  xlim(-1, 1)
```


Plot shape and actin s.d. together
```{r}

inner_join(shape %>% rename(shape = value), 
           actin_sd %>% rename(actin_sd = value)) %>%
  gather(predictor, value, -FeatureIdx) %>%
  ggplot(aes(value, fill = predictor)) + 
  stat_density(adjust = 0.8, alpha = 0.3) + 
  xlab("Adjusted R^2 of prediction Actin total intensity given a predictor") + 
  xlim(-1, 1)
```

